---
title: "Regression Model Course Project"
author: "Sebastian Jaroszewicz"
date: "12/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The objective of this study is to ooking at a data set of a collection of cars and to explore the relationship between a set of variables and miles per gallon (MPG) (outcome). In particular it is of interest to answer the following questions:

* “Is an automatic or manual transmission better for MPG”
* "Quantify the MPG difference between automatic and manual transmissions"

The data set that will be used to carry out the study will be the \textcolor{red}{mtcars}.

## Exploratory Data Analysis

```{r analysis}
library(ggplot2)

data(mtcars)
head(mtcars)
str(mtcars)
```
The data set is composed of with 32 observations on 11 (numeric) variables.

1.	mpg	Miles/(US) gallon
2.	cyl	Number of cylinders
3.	disp	Displacement (cu.in.)
4.	hp	Gross horsepower
5.	drat	Rear axle ratio
6.	wt	Weight (1000 lbs)
7.	qsec	1/4 mile time
8.	vs	Engine (0 = V-shaped, 1 = straight)
9.	am	Transmission (0 = automatic, 1 = manual)
10.	gear	Number of forward gears
11.	carb	Number of carburetors

```{r factors}
# Transform same varialbes into factor
mtcars$am <- factor(mtcars$am,labels=c("Automatic","Manual"))
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```


