---
title: "Regression Model Course Project"
author: "Sebastian Jaroszewicz"
date: "12/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The objective of this study is to ooking at a data set of a collection of cars and to explore the relationship between a set of variables and miles per gallon (MPG) (outcome). In particular it is of interest to answer the following questions:

* “Is an automatic or manual transmission better for MPG”
* "Quantify the MPG difference between automatic and manual transmissions"

The data set that will be used to carry out the study will be the \textcolor{red}{mtcars}.

## Exploratory Data Analysis

```{r analysis}
library(ggplot2)
data(mtcars)
head(mtcars,3)
a <- dim(mtcars)
```
The data set is composed of with `r a[1]` observations on `r a[2]` (numeric) variables.

1.	mpg	Miles/(US) gallon
2.	cyl	Number of cylinders
3.	disp	Displacement (cu.in.)
4.	hp	Gross horsepower
5.	drat	Rear axle ratio
6.	wt	Weight (1000 lbs)
7.	qsec	1/4 mile time
8.	vs	Engine (0 = V-shaped, 1 = straight)
9.	am	Transmission (0 = automatic, 1 = manual)
10.	gear	Number of forward gears
11.	carb	Number of carburetors

```{r factors}
# Transform same varialbes into factor
mtcars$am <- factor(mtcars$am,labels=c("Automatic","Manual"))
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$gear <- as.factor(mtcars$gear)
mtcars$carb <- as.factor(mtcars$carb)
```
In order to better understand the data, we made a box plot graph  mpg by tansmission type (see appendix).


The plot shows a significant difference between manual and automatic transmissions. To quantitatively analyze this difference we are going to perform a t-test
```{r t_test}
testResults <- t.test(mtcars$mpg ~ mtcars$am)
testResults
```
The T-Test rejects the null hypothesis that the difference between transmission
types is 0. The difference estimate between the 2 transmissions is about 7 mpg in favor of the manual.

## Regression Model
To study the relationship between mpg and the other variables, we performed a regression model for this dataset. We use multiple linear regression and the R step function, which chooses the best model.

```{r regression, eval=FALSE}
fit <- lm(mpg~.,mtcars) 
summary(fit)
fit_Step <- step(fit)
```
The model suggest to use the formula **mpg ~ cyl + hp + wt + am**
```{r call}
model = lm(mpg~ wt + qsec + am, data=mtcars)
summary(model)
```
In th appendix we plot the residuals of the model.

## Conclusions
From our study we can determine that there is a difference in mpg in relation to transmission type in favor of manual. But a better explanation adjust with weight and qsec.

## Appendix


```{r box_plot}
#boxplot(mpg ~ am, data = mtcars, col = (c("red","blue")), ylab = "Miles Per Gallon", xlab = "Transmission Type")
g <- ggplot(mtcars, aes(x=am, y=mpg, color = am)) + 
          geom_boxplot()
g <- g + geom_jitter(shape=16, position=position_jitter(0.2))
g
```
```{r residuals}
ggplot(model, aes(.fitted, .resid)) + geom_point() +
  stat_smooth(method="loess", col="steelblue") + geom_hline(yintercept=0, linetype="dashed") +
  xlab("Fitted values")+ylab("Residuals") + 
  ggtitle("Residual vs Fitted Plot") + theme_bw()
```